---
title: "2019-01-08_TVs-Golden-Age"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(here)
ratings_raw <- read_csv(here("data/2019/2019-01-08/IMDb_Economist_tv_ratings.csv"))
ratings_raw
```

# Exploration

Let's see what the genres look like. 
```{r}
ratings_raw %>% 
  filter(str_detect(genres, "Drama")) %>% 
  count()
```

Okay, so every row contains the word "Drama".

How many unique genre entries are there?
```{r}
length(unique(ratings_raw$genres))
```

97 - a lot.


## What the heck is "share"?

According to the #tidytuesday folks, it's "share of IMDb ratings for shows in that year". Let's see if that makes sense.

```{r}
ratings_raw %>% 
  mutate(year = lubridate::year(date)) %>% 
  group_by(year) %>% 
  summarise(share_sum = sum(share))
```

Okay, this makes sense then. 

```{r}
hist(ratings_raw$share)
ratings_raw %>% 
  ggplot(aes(share)) +
  geom_freqpoly()

```

What is the relationship between share and ratings?
```{r}
ratings_raw %>% 
  ggplot(aes(x = av_rating, y = share)) +
  geom_point(alpha = 0.2)
```



## Ratings

Let's try a fun plot to see ratings over time.

```{r}
ratings_raw  %>%  
  ggplot(aes(date, av_rating)) +
  geom_point()
```

What if I want to see a line for each show, connecting the seasons, on the above?

```{r}
ratings_raw %>% 
  ggplot(aes(x = date, y = av_rating)) +
  geom_line(aes(group = title), alpha = 0.2) +
  geom_smooth(method = "lm")
```


# Spread out the genres to binary variables
The genre variable contains many different combinations of words. Try to parse this out to make each genre its own variable (boolean).

```{r}
# test <- ratings_raw$genres[1]
# unlist(str_split(test, ","))
genre_vector <- character()
for (i in 1:nrow(ratings_raw)) {
  x <- unlist(str_split(ratings_raw$genres[i], ","))
  for(j in 1:length(x)) {
    if(x[j] %in% genre_vector) {
      next
    } else {
      genre_vector <- c(genre_vector, x[j])
    }
  }
}

ratings <- ratings_raw
ratings <- tibble(matrix(data = NA, 
                         nrow = nrow(ratings), 
                         ncol = length(genre_vector))
)
```

