---
title: "Nuclear Explorsions - 01"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(janitor)
library(lubridate)
library(here)

df_raw <- read_csv(here("data/2019/2019-08-20/nuclear_explosions.csv"))

glimpse(df_raw)

```

# Preprocessing and data clean
The `date_long` variable hasn't been parsed correctly. Let's fix that.
```{r}
df <- df_raw %>% 
  mutate(date_long = lubridate::as_date(as.character(df_raw$date_long)),
         country = as_factor(country),
         region = as_factor(region),
         source = as_factor(source),
         purpose = as_factor(purpose),
         type = as_factor(type))

glimpse(df)
```


# Have a first look around

What are some of the "others" in the factor categories, such as `type`, `purpose`, `source` and `region`? Are there tons of other entries or just a lot of a few?

```{r}
df %>% 
  group_by(purpose) %>% 
  count() %>% 
  arrange(n)
```

For `purpose` there are several possible variables that can be combined, so these should be spread out accross columns of dummy variables.

```{r}
df %>% 
  group_by(source) %>% 
  count() %>% 
  arrange(n)
```

```{r}
df %>% 
  group_by(region) %>% 
  count() %>% 
  arrange(n)
```


### What is the relationship between `magnitude_body` and `magnitude_surface`?

```{r}
df %>% 
  ggplot(aes(x = magnitude_body, y = magnitude_surface)) +
  geom_point()
```

### How has the yield changed over time (is this "power")?

```{r}
df %>% 
  select(date_long, yield_lower, yield_upper) %>% 
  gather(key = "type", value = "yield", -date_long) %>%
  ggplot(aes(x = date_long, y = log(yield), colour = type)) +
  geom_point(size = 0.1)
```

